A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-04 paper.tex
OK, Fig 2 only has three tools

\ctable[caption={A comparison of the VABC descriptor for molecular
  volume (as implemented by the CDK) and other approximate
  implementations of molecular volume (as implemented by MOE 2008.10)},cap={},label={fig:molvol},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{vol-moe-cdk}
}

\ctable[caption={Four tools to calculate descriptors: Bioclipse (top left), which allows selecting descriptor
implementations from various independent tools, CDK-Taverna (top right), which is an extension to Taverna
to calculate descriptors with the CDK, Ambit2 (bottom left), which implements the OpenTox API providing
a REST-based API for descriptor calculation and wraps various descriptor calculation tools,
and ....},cap={},label={fig:tools},botcap,figure]
{c}
{}
{
  \includegraphics[width=0.48\linewidth]{bioclipse}
  \includegraphics[width=0.48\linewidth]{cdktaverna} \\
  \includegraphics[width=0.48\linewidth]{ambitOnline}
}

@@

\ctable[caption={A comparison of Topological Polar Surface Area values
generated using the CDK and ACD Labs software, for 57,857 molecules
taken from Pubchem AID 1996},cap={},label={fig:tpsa},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{tpsa-cdk-acd}
}

>>>>

\ctable[caption={A comparison of the VABC descriptor for molecular
  volume (as implemented by the CDK) and other approximate
  implementations of molecular volume (as implemented by MOE 2008.10).},cap={},label={fig:molvol},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{vol-moe-cdk}
}

\ctable[caption={Three tools to calculate descriptors: Bioclipse (top left), which allows selecting descriptor
implementations from various independent tools, CDK-Taverna (top right), which is an extension to Taverna
to calculate descriptors with the CDK, Ambit2 (bottom), which implements the OpenTox API providing
a REST-based API for descriptor calculation and wraps various descriptor calculation
tools.},cap={},label={fig:tools},botcap,figure]
{c}
{}
{
  \includegraphics[width=0.48\linewidth]{bioclipse}
  \includegraphics[width=0.48\linewidth]{cdktaverna} \\
  \includegraphics[width=0.48\linewidth]{ambitOnline}
}

@@

\ctable[caption={A comparison of Topological Polar Surface Area values
generated using the CDK and ACD Labs software, for 57,857 molecules
taken from Pubchem AID 1996.},cap={},label={fig:tpsa},botcap,figure]
{c}
{}
{
  \includegraphics[width=\linewidth]{tpsa-cdk-acd}
}
